\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-23 paper/examples.tex
fix: meaning of alpha is swapped under new cost model

She indicates her preference for performance or for accuracy by providing a configuration parameter $\alpha$ to ImputeDB in addition to her query.
$\alpha$ is a dimensionless parameter in $[0,1]$, and it indicates the relative importance of the quality of query results and of query performance.
So, a low $\alpha$ results in a fast query plan that may compromise accuracy, while a high $\alpha$ results in a high quality query plan that may take longer to run.
In our intended workflow, the analyst picks a value of $\alpha$ and incrementally increases it to increase query result quality until the query takes too long to run.
Fig.~\ref{fig:quality-plan} and Fig.~\ref{fig:fast-plan} show plans for the example query in Fig.~\ref{fig:example-query} when optimizing for quality and performance, respectively.

@@

\begin{figure}
  \begin{subfigure}[b]{\linewidth}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\mu_{\text{demo.income}}$}
        [.$\bowtie_{\text{exams.id} = \text{demo.id}}$
          [.\colorbox{pink}{$\mu_{\text{labs.white\_blood\_cell\_ct}}$}
            [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
              [.$\sigma_{\text{exams.weight} \geq 120}$ 
                [.\colorbox{pink}{$\mu_{\text{exams.weight}}$} exams ] 
              ] 
              labs 
            ]
          ]
        [.$\sigma_{\text{demo.gender} = 2}$ demo ]
      ] 
    ] 
  ] 
  ]
  \caption{A plan for the query in Fig.~\ref{fig:example-query}, optimized for quality ($\alpha=1$).}
  \label{fig:quality-plan}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\delta_{\text{demo.income, labs.white\_blood\_cell\_ct}}$}
        [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
          [.$\bowtie_{\text{demo.id} = \text{exams.id}}$
            [.$\sigma_{\text{demo.gender} = 2}$ demo ]
            [.$\sigma_{\text{exams.weight} \geq 120}$ [.\colorbox{pink}{$\delta_{\text{exams.weight}}$} exams ] ] ] labs ] ] ] ]
\caption{A plan for the query in Fig.~\ref{fig:example-query}, optimized for performance ($\alpha=0$).}
\label{fig:fast-plan}
\end{subfigure}
\vspace{0.5\baselineskip}
\caption{Plans for the query in Fig.~\ref{fig:example-query}. Imputation operators are highlighted.}
\end{figure}

>>>>

She indicates her preference for performance or for accuracy by providing a configuration parameter $\alpha$ to ImputeDB in addition to her query.
$\alpha$ is a dimensionless parameter in $[0,1]$, and it indicates the relative importance of the quality of query results and of query performance.
So, a high $\alpha$ results in a fast query plan that may compromise accuracy, while a low $\alpha$ results in a high quality query plan that may take longer to run.
In our intended workflow, the analyst picks a value of $\alpha$ and incrementally increases it to increase query result quality until the query takes too long to run.
Fig.~\ref{fig:quality-plan} and Fig.~\ref{fig:fast-plan} show plans for the example query in Fig.~\ref{fig:example-query} when optimizing for quality and performance, respectively.

@@

\begin{figure}
  \begin{subfigure}[b]{\linewidth}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\mu_{\text{demo.income}}$}
        [.$\bowtie_{\text{exams.id} = \text{demo.id}}$
          [.\colorbox{pink}{$\mu_{\text{labs.white\_blood\_cell\_ct}}$}
            [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
              [.$\sigma_{\text{exams.weight} \geq 120}$ 
                [.\colorbox{pink}{$\mu_{\text{exams.weight}}$} exams ] 
              ] 
              labs 
            ]
          ]
        [.$\sigma_{\text{demo.gender} = 2}$ demo ]
      ] 
    ] 
  ] 
  ]
  \caption{A plan for the query in Fig.~\ref{fig:example-query}, optimized for quality ($\alpha=0$).}
  \label{fig:quality-plan}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
  \Tree
  [.$\pi_{\text{income, AVG(white\_blood\_cell\_ct)}}$
    [.$g_{\text{income, AVG(white\_blood\_cell\_ct)}}$
      [.\colorbox{pink}{$\delta_{\text{demo.income, labs.white\_blood\_cell\_ct}}$}
        [.$\bowtie_{\text{exams.id} = \text{labs.id}}$
          [.$\bowtie_{\text{demo.id} = \text{exams.id}}$
            [.$\sigma_{\text{demo.gender} = 2}$ demo ]
            [.$\sigma_{\text{exams.weight} \geq 120}$ [.\colorbox{pink}{$\delta_{\text{exams.weight}}$} exams ] ] ] labs ] ] ] ]
\caption{A plan for the query in Fig.~\ref{fig:example-query}, optimized for performance ($\alpha=1$).}
\label{fig:fast-plan}
\end{subfigure}
\vspace{0.5\baselineskip}
\caption{Plans for the query in Fig.~\ref{fig:example-query}. Imputation operators are highlighted.}
\end{figure}
